Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-20 article.tex
some modifs

\textcolor{red}{AJ: GENI3 is not on the figure}
As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance
increases with deeper trees in addition to be computationally feasible. The
reason is twofold. First, the deeper the tree, the larger is the conditioning.
As it was observed in the comparison between correlation and partial
correlation, it screens indirect links in the inferred network. Second, the
number of small trees need to be much higher than deep trees in order to
observe - and evaluate - all pairs.  However, as suggested by
\cite{louppe2014understanding}, limiting the maximal depth of trees may help
to reduce the misestimation bias in variable importance computing, i.e.
inferring the strength of a link. Therefore a trade-off of the maximal depth
may give the best of both worlds.

@@

In this paper, we present the winning method of the Connectomics challenge.
This approach is simple and theoretically grounded. We also evaluate the method
in a more detailed way and perform a comparison with other inference methods.
We also discuss the relevance of the metric used in the challenge.

In the discussion, we give hints about limiting the depth of trees in the
GENIE3 method to infer the network. It should be interesting to see if there
is a optimum value for the maximal depth. And of course, it may also rewarding
to increase considerably the number of trees to get more stable predictions.

In previous study \citep{shipley2002cause}, it has been suggested to
consider correlation coefficients of all possible orders,
i.e. conditioned on every subsets of the set of $p-2$ other variables. This
would take into account multiple indirect paths between a given pair of
variables. Instead of considering only the highest order, it may be useful to
study with accuracy the inferred network at all orders. In this case, it may not
be very relevant but interesting in case of dynamical networks.

As we mentioned, in order to maximize the ROC AUC, it was not necessary to
discover causal relationships. It may be, in future works, promising to focus
on that particular topic.

>>>>

As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance
increases with deeper trees in addition to be computationally feasible. The
reason is twofold. First, the deeper the tree, the larger is the conditioning.
As it was observed in the comparison between correlation and partial
correlation, it screens indirect links in the inferred network. Second, the
number of small trees need to be much higher than deep trees in order to
observe - and evaluate - all pairs.  However, as suggested by
\cite{louppe2014understanding}, limiting the maximal depth of trees may help
to improve the variable importance computing, i.e.
inferring the degree of association. Therefore a trade-off of the maximal depth
may give the best of both worlds.

@@

In this paper, we present the winning method of the Connectomics challenge.
Our approach is simple and theoretically sounded and made of two main stages: the signal is first preprocessed with several filters and then we derive the degree of association matrix by computing the partial correlation statistics matrix. We also evaluate the method
in a more detailed way and perform a comparison with other inference methods.
We finally discuss the relevance of the metric used in the challenge and we point out that it was not necessary to
discover causal relationships to maximize the ROC AUC. Thus, it may be  promising to focus
on that particular topic in future works.

% In the discussion, we give hints about limiting the depth of trees in the
% GENIE3 method to infer the network. It should be interesting to see if there
% is a optimum value for the maximal depth. And of course, it may also rewarding
% to increase considerably the number of trees to get more stable predictions.

% In previous study \citep{shipley2002cause}, it has been suggested to
% consider correlation coefficients of all possible orders,
% i.e. conditioned on every subsets of the set of $p-2$ other variables. This
% would take into account multiple indirect paths between a given pair of
% variables. Instead of considering only the highest order, it may be useful to
% study with accuracy the inferred network at all orders. In this case, it may not
% be very relevant but interesting in case of dynamical networks.

% As we mentioned, in order to maximize the ROC AUC, it was not necessary to
% discover causal relationships. It may be, in future works, promising to focus
% on that particular topic.
